The title

### 2024-08-27 05_Manuscript/manuscript.Rmd
here's stuff

```{r libraries}
library(rio)
library(dplyr)
set.seed(8943)
```

```{r load-data}
sona <- import("../03_Data/sona_data.csv")
mturk <- import("../03_Data/mturk_data.csv")
```

>>>>

```{r libraries}
library(rio)
library(dplyr)
set.seed(8943)
library(mice)

## args: dat: Dataframe of scale values, with each row being a participant and each column being a scale question
## args: rt: vector of response time/page time for each participant
## args: min: minimum value of scale
## args: max: maximum value of scale
## args: partno: vector of corresponding participant numbers
## args: clicks: click count column, outputted by qualtrics
## args: manvec: vector of manipulation check question responses
## args: mancor: correct answer of manipulation check
## args: char: number of characters on the page

SAD <- function(dat, #data frame of only scale values
               rt = NULL, #column name for page timing
               min = 1, #lower end of scale points
               max = 7, #upper end of scale points
               partno, #participant number so you can merge and identify outliers
               click = NULL, #column of click counts
               manvec = NULL, #column of manipulation check
               mancor = NULL, #answer to the manipulation check
               char = NULL){ #number of characters on the page

  ##make sure the data provided is a data frame
  dat = as.data.frame(dat)

  ####number of scale options used####
  OptUse = function(x){
    length(table(as.vector(as.matrix(unname(x)))))
  }
  numOpt = apply(dat,1,OptUse)
  numOpt = as.numeric(numOpt)
  nsim = length(numOpt)
  badScaleCheck = rep(NA, length(numOpt))
  for(i in 1:nsim){
    ##more than half of the options
    optionhalf = length(min:max)/2+1
    if(numOpt[i] >= optionhalf){
      badScaleCheck[i] = 1
    } else { badScaleCheck[i] = 0 }
  }
  badScaleCheck = as.numeric(badScaleCheck)

  ####response/page time####
  if (!is.null(rt)){
    rt = as.numeric(unlist(rt))

    ourchar = char
    meanchar = 987
    sdchar = 118
    upperchar = meanchar + 2*sdchar
    cutoffChar = ourchar / upperchar * 60
    badChar = rep(NA, length(rt))
    nsim = length(badChar)
    for(i in 1:nsim){
      if(!is.na(rt[i])){
        if(rt[i] < cutoffChar){
          badChar[i] = 1
        } else{
          badChar[i] = 0
        }
      } else { badChar[i] = NA}
    }
    badChar = as.numeric(badChar)
  } else { badChar = rep(NA, nrow(dat))}

  ####click count check####
  if(!is.null(click)){
    click = as.numeric(unlist(click))
    totalexp = apply(dat,1, function(x){sum(!is.na(x))})
    nsim = length(click)
    badClick = rep(NA, length(click))
    for(i in 1:nsim){
      if(!is.na(click[i])){
        if(click[i] >= totalexp[i]){
          badClick[i] = 0
        } else{
          badClick[i] = 1
        }
      } else{ badClick[i] = NA}
    }
    badClick = as.numeric(badClick)
  } else { badClick = rep(NA, nrow(dat))}

  ####manipulation check question manip####
  if(!is.null(manvec)){
    manvec = as.numeric(unlist(manvec))
    nsim = length(manvec)
    badMC = rep(NA, nrow(dat))
    for(i in 1:nsim){
      if(!is.na(manvec[i])){ 
        if(manvec[i] == mancor) { badMC[i] = 0 } else { badMC[i] = 1}} else { badMC[i] = 1}
    }
    badMC = as.numeric(badMC)
  } else { badMC = rep(NA, nrow(dat))}

  ####Distribution Testing####
  uniform = rep(NA,nrow(dat))
  normal = rep(NA, nrow(dat))
  dist = rep(NA, nrow(dat))
  nsim = nrow(dat)
  for(i in 1:nsim){
    temprow = as.numeric(unname(dat[i,])) 
    utable = matrix(0, nrow = 1, ncol = length(min:max))
    for(x in min:max) {
      utable[x] = length(temprow[ temprow == x])
    }
    uniformest = chisq.test(utable,
                            rescale.p = T,
                            simulate.p.value = T)
    ##test normal distribution
    ##first convert to z score
    ztest = scale(temprow)
    ##then figure out how much of the data is binned for SDs
    ztable = matrix(0, nrow = 1, ncol = 6)
    ztable[1] = length(ztest[ ztest <= -2 ])  
    ztable[2] = length(ztest[ ztest > -2 & ztest <= -1  ])
    ztable[3] = length(ztest[ ztest > -1 & ztest <= 0 ])
    ztable[4] = length(ztest[ ztest > 0 & ztest <= 1 ])
    ztable[5] = length(ztest[ ztest > 1 & ztest <= 2 ])
    ztable[6] = length(ztest[ ztest > 2 ])
    znormal = c(0.0228, 0.1359, 0.3413, 0.3413, 0.1359, 0.0228)
    normalest = chisq.test(ztable,
                           p = znormal*sum(ztable),
                           rescale.p = T,
                           simulate.p.value = T)
    ##output return chi square values
    uniform[i] = uniformest$statistic
    normal[i] = normalest$statistic
    ##if uniform < normal
    if(uniformest$statistic < normalest$statistic)
    {
      ##if more than 1 option
      if (numOpt[i]>1)
      {
        dist[i] = 0 ##uniform is better
      } else { ##handles when people only pick one thing
        dist[i] = 2
      }
    }
    ##if uniform >= normal
    if(uniformest$statistic >= normalest$statistic)
    {
      ##if more than 1 option
      if (numOpt[i]>1)
      {
        dist[i] = 1 ##normal is better
      } else { ##handles when people only pick one thing
        dist[i] = 2
      }

    }
    #0 means uniform fits better
    #1 means normal fits better
    #2 means only chose one scale option
  }## end of for loop

  ####distribution coding####
  badDist = rep(NA, nsim)
  for(i in 1:nsim){
    if(dist[i] == 0){
      badDist[i] = 1
    } 
    if (dist[i] == 1){
      badDist[i] = 0
    } 
    if (dist[i] == 2) {
      badDist[i] = 0
    }
  }
  badDist = as.numeric(badDist)

  ####total up####
  badDF = cbind.data.frame(badChar, badClick, badDist, badScaleCheck, badMC)
  badDF$badTotal = apply(badDF, 1, sum, na.rm = T)
  badDF$participant = partno

  return(badDF)

} #end function

percentmiss <- function(x){ sum(is.na(x))/length(x) *100 }
```

```{r load-data, eval = T}
sona <- import("../03_Data/sona_data_deidentify.csv") %>% 
  mutate(where = "sona")
mturk <- import("../03_Data/mturk_data_deidentify.csv") %>% 
  mutate(where = "mturk")
```

## Data Screening

```{r screen-sona-accuracy-out, eval = F}
# Accuracy ----
summary(sona %>% 
          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20))
# everything is within the expected range

apply(sona %>% 
          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
      2, mean, na.rm = TRUE)
apply(sona %>% 
          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
      2, sd, na.rm = TRUE)
# check reverse items? Q2_21?

# Missing ----

# rows
missing <- apply(sona %>% 
          select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
          1, 
          percentmiss) 
table(missing)
replacepeople <- subset(sona, missing <= 5)
dontpeople <- subset(sona, missing > 5)

# columns
missingcol <- apply(replacepeople %>% 
                      select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20), 
                    2, 
                    percentmiss)
table(missingcol) # all replaceable

replacecolumn <- replacepeople %>% 
  select(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20)
dontcolumn <- replacepeople %>% 
  select(-c(Q2_1:Q2_21, Q4_1:Q4_20, Q5_1:Q5_20))

# replacing those with <= 5% missing by multiple imputation
tempnomiss <- mice(replacecolumn)
nomiss <- complete(tempnomiss, 1)
summary(nomiss)

# putting data back together
# excluding participants with > 5% missing (7 total)
allcolumns <- cbind(dontcolumn, nomiss)
summary(allcolumns)
write.csv(allcolumns, "../03_Data/sona_data_replaced.csv", row.names = F)
```

```{r screen-sona-SAD}
# SAD 
nomissing <- import("../03_Data/sona_data_replaced.csv")

# Block 1
page1 <- SAD(dat = nomissing %>% 
               select(Q2_1:Q2_21),
    rt = nomissing$`Q10_Page Submit`,
    min = 1, 
    max = 5, 
    partno = nomissing$ResponseId, 
    click = nomissing$`Q10_Click Count`, 
    manvec = nomissing$Q2_21, 
    mancor = 1, 
    char = 1626)
write.csv(page1, "../03_Data/sona_page1_sad.csv", row.names = F)

# Block 2
page2 <- SAD(dat = nomissing %>% 
               select(Q4_1:Q4_20), 
            rt = nomissing$`Q11_Page Submit`,
            min = 1, 
            max = 5, 
            partno = nomissing$ResponseId, 
            click = nomissing$`Q11_Click Count`, 
            manvec = nomissing$Q4_20, 
            mancor = 4, 
            char = 1491)
write.csv(page2, "../03_Data/sona_page2_sad.csv", row.names = F)

# Block 3
page3 <- SAD(dat = nomissing %>% 
               select(Q5_1:Q5_20), 
            rt = nomissing$`Q12_Page Submit`,
            min = 1, 
            max = 5, 
            partno = nomissing$ResponseId, 
            click = nomissing$`Q12_Click Count`, 
            manvec = nomissing$Q5_16, 
            mancor = 3, 
            char = 1496)
write.csv(page3, "../03_Data/sona_page3_sad.csv", row.names = F)

# Total
nomissing$totalbad <- page1$badTotal + page2$badTotal + page3$badTotal

nomissing$totalbadUP = 
  page1$badChar + page1$badClick + page1$badMC + 
  page2$badChar + page2$badClick + page2$badMC + 
  page3$badChar + page3$badClick + page3$badMC
table(nomissing$totalbadUP)
nolowqual = subset(nomissing, totalbadUP < 4)
##B&S say 2/5 which is 40%, so 40% of the 9 total is 3.6 or 4 or more

# Outliers ----------------------------------------------------------------

mahal = mahalanobis(nolowqual[ , 37:97], 
                    colMeans(nolowqual[ , 37:97], na.rm = TRUE),
                    cov(nolowqual[ , 37:97], use="pairwise.complete.obs"))

cutoff = qchisq(1 - .001,ncol(nolowqual[ , 37:97]))
ncol(nolowqual[ , 37:97]) #df 61
cutoff #cutoff 100.8879

summary(mahal < cutoff)
mahal[mahal > cutoff]

noout = subset(nolowqual, mahal < cutoff)
#42 participants excluded as outliers

# Assumptions -------------------------------------------------------------

# Linearity #
random = rchisq(nrow(noout[ , 37:97]), 7) 
fake = lm(random~., data=noout[ , 37:97])

standardized = rstudent(fake)
{qqnorm(standardized)
  abline(0,1)}
#seems okay

# Normality #
hist(standardized, breaks=15)
#a little skewed but mostly centered on 0 and between -2 and 2 so okay

# Homog/s #
fitvalues = scale(fake$fitted.values)
{plot(fitvalues, standardized) 
  abline(0,0)
  abline(v = 0)}
#some homogeneity issues but we'll accept it

write.csv(noout, file = "sona_data_screened.csv", row.names = F)
library(beepr)
beep(sound = 5)

# > nrow(master)
# [1] 564
# > nrow(nomissing)
# [1] 557
# > nrow(nolowqual)
# [1] 507
# > nrow(noout)
# [1] 464

sona_screen_1 <- SAD(
  dat = sona %>% 
    select(Q2_1:Q2_21, `Q10_Page Submit`, `Q10_Click Count`),
  rt = "Q10_Page Submit",
  min = 1,
  max = 5, 
  partno = "ResponseId",
  clicks = "Q10_Click Count",

)

## args: dat: Dataframe of scale values, with each row being a participant and each column being a scale question
## args: rt: vector of response time/page time for each participant
## args: min: minimum value of scale
## args: max: maximum value of scale
## args: partno: vector of corresponding participant numbers
## args: clicks: click count column, outputted by qualtrics
## args: manvec: vector of manipulation check question responses
## args: mancor: correct answer of manipulation check
## args: char: number of characters on the page
```
